Solution of near-Toeplitz tridiagonal systems on GPU-accelerated clusters

### 2016-03-24 paper-draft/paper.tex
add some more notes to the conclusions

In Fig. \ref{fig:bench-2d} and \ref{fig:bench-3d},
we provide the relative performance of
Intel MKL and CUSPARSE solvers and compare against
the NEATO shared memory implementation.
The relative performance for
each problem size is obtained by
normalizing the solver timings
by the timing for the fastest solver for that problem size.
Table \ref{table:bench} shows the timings of the various
solvers to solve different problem sizes.

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
\hl{These are the same for all local grid lines,
so they are \emph{precomputed} -
solved \emph{once} for a single local grid line in each subdomain.}

@@

We present a GPU solver for \emph{near-Toeplitz} tridiagonal systems
based on the cyclic reduction algorithm,
that is applicable to several numerical schemes
in computational fluid dynamics.
Our solver gives better performance than
the current multicore Intel MKL and CUSPARSE solvers
Additionally, we describe an implementation of our solver
for GPU clusters,
and provide performance results for a
compact finite difference application,
run on up to 64 GPUs.

>>>>

In Fig. \ref{fig:bench-2d} and \ref{fig:bench-3d},
we provide the relative performance of
Intel MKL and CUSPARSE solvers and compare against
the NEATO shared memory implementation.
The relative performance for
each problem size is obtained by
normalizing the solver timings
by the timing for the fastest solver for that problem size.
Table \ref{table:bench} shows the timings of the various
solvers to solve different problem sizes.
\hl{
We note that NEATO performs
at least as well as the Intel MKL on 8-16 cores
for most cases,
and outperforms CUSPARSE in almost all cases.
This is primarily because NEATO is able to take advantage
of the known matrix coefficients,
while the CUSPARSE implementation is for the more
general tridigaonal case.
}

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
\hl{These are the same for all local grid lines,
so they are solved \emph{once} for a single local grid line in each subdomain.
The results are stored on the GPU and reused for other grid lines.}

@@

We present a GPU solver for \emph{near-Toeplitz} tridiagonal systems
based on the cyclic reduction algorithm,
that is applicable to several numerical schemes
in computational fluid dynamics.
\hl{Our solver is able to take advantage of the
special structure of these systems
to reduce the number of computations performed and
improve memory access patterns.
Thus, we are able to show better performance
compared to the Intel MKL and NVIDIA CUSPARSE solvers
on multi-core CPUs and GPUs respectively.}
Additionally, we describe an implementation of our solver
for multi-GPU clusters,
and provide performance results for a
compact finite difference application,
run on up to 64 GPUs.
